---
title: "Data and datasets"
author: "admin"
date: "10/4/2021"
output: html_document
---

First, we load the datasets and tidyverse.
```{r setup, include=FALSE}
library(fivethirtyeight)
library(tidyverse)
```

Now, we call the specific dataset within `fivethirtyeight` for us to clean and analyse. Here, let's call `comma_survey`  which looks at American's attitudes towards the Oxford comma.

```{r}
colnames(comma_survey)
```

Now let's look at a tibble and how the data is generally structured. 

```{r}
head(comma_survey, 10)

```
Let's first try `filter`
```{r}
filter(comma_survey, gender == "Male")
```

`Arrange` 

```{r}
arrange(comma_survey, household_income)
arrange(comma_survey, desc(age))
```

```{r}
select(comma_survey, gender, age)
```
```{r}
select(comma_survey, gender:education)
```
```{r}
select(comma_survey, -(gender:education))
```

```{r}
rename(comma_survey, ageiny = age)
```

Let's look at pipes, which basically makes things a lot more easier and honestly, faster.

```{r}
comma_survey<-comma_survey %>%
  group_by(location)%>%
  rename(inc=household_income)
colnames(comma_survey)
``
